R Notebook

### 2022-09-17 create-paper-figures.Rmd
supplement revisions

```{r}
# In Experiment 1, like participants' responses,  the model's estimates are very slightly positive for {icy, frosty} and very slightly negative for {normal, typical}. This pattern replicates the qualitative pattern reported by Zhu and colleagues.
plt_ineq_exp1 + labs(title="Exp. 1") + 
  plt_ineq_exp2 + labs(title="Exp. 2") + 
  plot_layout(guides="collect") & theme(legend.position="bottom") & labs(color="", y = "Estimate", x = "Identity")
```

@@

```{r}
plt_dk_ptn1 <- py$posterior_ptn1 %>% 
    group_by(ID) %>% 
    summarize(
        k_est = mean(k),
        k_ll = quantile(k, .05),
        k_ul = quantile(k, .95),
        d_est = mean(d_subj),
        d_ll = quantile(d_subj, .05),
        d_ul = quantile(d_subj, .95)
    ) %>% 
#     s.filter(_.k_est < 50.) >>
    filter(ID!=51, ID!=45, ID!=29, ID!=28) %>% 
    ggplot(aes(x=k_est, y=d_est)) +
    geom_point() +
    geom_errorbar(aes(ymin=d_ll, ymax=d_ul), width=0., alpha=.25) +
    geom_errorbarh(aes(xmin=k_ll, xmax=k_ul), height=0, alpha=.25) +
    # geom_smooth(method="lm") +
    labs(y="d", x="k", title="Exp. 1") +
    theme_bw() +
    theme(aspect.ratio=1) +
    theme(panel.grid = element_blank())

plt_dk_ptn2 <- py$posterior_ptn2 %>% 
    group_by(ID) %>% 
    summarize(
        k_est = mean(k),
        k_ll = quantile(k, .05),
        k_ul = quantile(k, .95),
        d_est = mean(d_subj),
        d_ll = quantile(d_subj, .05),
        d_ul = quantile(d_subj, .95)
    ) %>% 
#     s.filter(_.k_est < 50.) >>
    # filter(ID!=51, ID!=45, ID!=29, ID!=28) %>% 
    ggplot(aes(x=k_est, y=d_est)) +
    geom_point() +
    geom_errorbar(aes(ymin=d_ll, ymax=d_ul), width=0., alpha=.25) +
    geom_errorbarh(aes(xmin=k_ll, xmax=k_ul), height=0, alpha=.25) +
    # geom_smooth(method="lm") +
    labs(y="d", x="k", title="Exp. 2") +
    theme_bw() +
    theme(aspect.ratio=1) +
    theme(panel.grid = element_blank())

plt_dprimek_ptn1 <- py$posterior_ptn1 %>% 
    group_by(ID) %>% 
    summarize(
        k_est = mean(k),
        k_ll = quantile(k, .05),
        k_ul = quantile(k, .95),
        d_est = mean(d_prime_subj),
        d_ll = quantile(d_prime_subj, .05),
        d_ul = quantile(d_prime_subj, .95)
    ) %>% 
#     s.filter(_.k_est < 50.) >>
    filter(ID!=51, ID!=45, ID!=29, ID!=28) %>% 
    ggplot(aes(x=k_est, y=d_est)) +
    geom_point() +
    geom_errorbar(aes(ymin=d_ll, ymax=d_ul), width=0., alpha=.25) +
    geom_errorbarh(aes(xmin=k_ll, xmax=k_ul), height=0, alpha=.25) +
    # geom_smooth(method="lm") +
    labs(y="d'", x="k") +
    theme_bw() +
    theme(aspect.ratio=1) +
    theme(panel.grid = element_blank())

plt_dprimek_ptn2 <- py$posterior_ptn2 %>% 
    group_by(ID) %>% 
    summarize(
        k_est = mean(k),
        k_ll = quantile(k, .05),
        k_ul = quantile(k, .95),
        d_est = mean(d_prime_subj),
        d_ll = quantile(d_prime_subj, .05),
        d_ul = quantile(d_prime_subj, .95)
    ) %>% 
#     s.filter(_.k_est < 50.) >>
    # filter(ID!=51, ID!=45, ID!=29, ID!=28) %>% 
    ggplot(aes(x=k_est, y=d_est)) +
    geom_point() +
    geom_errorbar(aes(ymin=d_ll, ymax=d_ul), width=0., alpha=.25) +
    geom_errorbarh(aes(xmin=k_ll, xmax=k_ul), height=0, alpha=.25) +
    # geom_smooth(method="lm") +
    labs(y="d'", x="k") +
    theme_bw() +
    theme(aspect.ratio=1) +
    theme(panel.grid = element_blank())
```

>>>>

```{r}
# In Experiment 1, like participants' responses,  the model's estimates are very slightly positive for {icy, frosty} and very slightly negative for {normal, typical}. This pattern replicates the qualitative pattern reported by Zhu and colleagues.
plt_ineq_exp1 + labs(title="Exp. 1") + 
  plt_ineq_exp2 + labs(title="Exp. 2") + 
  plot_layout(guides="collect") & 
  theme(legend.position="bottom", axis.text.x = element_text(angle=90, hjust=1, vjust=.5)) & 
  labs(color="", y = "Estimate", x = "Identity")
```

@@

```{r}
plt_dk_ptn1 <- py$posterior_ptn1 %>% 
    group_by(ID) %>% 
    summarize(
        k_est = mean(k),
        k_ll = quantile(k, .05),
        k_ul = quantile(k, .95),
        d_est = mean(d_subj),
        d_ll = quantile(d_subj, .05),
        d_ul = quantile(d_subj, .95)
    ) %>% 
#     s.filter(_.k_est < 50.) >>
    filter(ID!=51, ID!=45, ID!=29, ID!=28) %>% 
    ggplot(aes(x=k_est, y=d_est)) +
    geom_point() +
    geom_errorbar(aes(ymin=d_ll, ymax=d_ul), width=0., alpha=.25) +
    geom_errorbarh(aes(xmin=k_ll, xmax=k_ul), height=0, alpha=.25) +
    # geom_smooth(method="lm") +
    labs(y="d", x="N", title="Exp. 1") +
    theme_bw() +
    theme(aspect.ratio=1) +
    theme(panel.grid = element_blank())

plt_dk_ptn2 <- py$posterior_ptn2 %>% 
    group_by(ID) %>% 
    summarize(
        k_est = mean(k),
        k_ll = quantile(k, .05),
        k_ul = quantile(k, .95),
        d_est = mean(d_subj),
        d_ll = quantile(d_subj, .05),
        d_ul = quantile(d_subj, .95)
    ) %>% 
#     s.filter(_.k_est < 50.) >>
    # filter(ID!=51, ID!=45, ID!=29, ID!=28) %>% 
    ggplot(aes(x=k_est, y=d_est)) +
    geom_point() +
    geom_errorbar(aes(ymin=d_ll, ymax=d_ul), width=0., alpha=.25) +
    geom_errorbarh(aes(xmin=k_ll, xmax=k_ul), height=0, alpha=.25) +
    # geom_smooth(method="lm") +
    labs(y="d", x="N", title="Exp. 2") +
    theme_bw() +
    theme(aspect.ratio=1) +
    theme(panel.grid = element_blank())

plt_dprimek_ptn1 <- py$posterior_ptn1 %>% 
    group_by(ID) %>% 
    summarize(
        k_est = mean(k),
        k_ll = quantile(k, .05),
        k_ul = quantile(k, .95),
        d_est = mean(d_prime_subj),
        d_ll = quantile(d_prime_subj, .05),
        d_ul = quantile(d_prime_subj, .95)
    ) %>% 
#     s.filter(_.k_est < 50.) >>
    filter(ID!=51, ID!=45, ID!=29, ID!=28) %>% 
    ggplot(aes(x=k_est, y=d_est)) +
    geom_point() +
    geom_errorbar(aes(ymin=d_ll, ymax=d_ul), width=0., alpha=.25) +
    geom_errorbarh(aes(xmin=k_ll, xmax=k_ul), height=0, alpha=.25) +
    # geom_smooth(method="lm") +
    labs(y="d'", x="N") +
    theme_bw() +
    theme(aspect.ratio=1) +
    theme(panel.grid = element_blank())

plt_dprimek_ptn2 <- py$posterior_ptn2 %>% 
    group_by(ID) %>% 
    summarize(
        k_est = mean(k),
        k_ll = quantile(k, .05),
        k_ul = quantile(k, .95),
        d_est = mean(d_prime_subj),
        d_ll = quantile(d_prime_subj, .05),
        d_ul = quantile(d_prime_subj, .95)
    ) %>% 
#     s.filter(_.k_est < 50.) >>
    # filter(ID!=51, ID!=45, ID!=29, ID!=28) %>% 
    ggplot(aes(x=k_est, y=d_est)) +
    geom_point() +
    geom_errorbar(aes(ymin=d_ll, ymax=d_ul), width=0., alpha=.25) +
    geom_errorbarh(aes(xmin=k_ll, xmax=k_ul), height=0, alpha=.25) +
    # geom_smooth(method="lm") +
    labs(y="d'", x="N") +
    theme_bw() +
    theme(aspect.ratio=1) +
    theme(panel.grid = element_blank())
```
